Real Time Adaptive Shape Reconstruction for Asteroid Landing

### 2018-04-05 manuscript.tex
Update sspi paper

\section{Asteroid Shape Modeling}
A polyhedron is a generalization of a two-dimensional polygon to three-dimensions.
It is the region of space with a boundary defined by a surface of a finite number of polygonal faces.
The surface of the polyhedron is composed of three types of primitive objects: zero-dimensional points called vertices, one-dimensional segments called edges, and two-dimensional polygons called faces or facets.
Furthemore, without any loss of generality we assume each face is a convex polygon since any nonconvex face can be divided into smaller convex faces.
A valid polyhedron in the context of asteroid shape models must satisfy several constraints.
These constraints define the relationship between each of the types of primitives which make up the polyhedron surface.
The primitives must intersect ``properly'', the local and global topology must be ``proper''.
For asteroid shape model we further assume that each face is a triangular polygon. 
Again, this does not limit generality as any polygon can be divided into a series of planar triangles.

@@

Summarize shape models for asteroids

Talk a little about polyhedra in geometry

Discuss the OBJ format and vertices and faces

>>>>

\section{Asteroid Shape Modeling}

Asteroids can have a wide variety of shapes, and most are vastly different than that of a sphere or ellipsoid.
\Cref{fig:irregular_asteroids} shows two examples of small solar system bodies that have highly irregular shapes.
As a result of these highly variable shapes, an adaptable format is required to represent the wide variety of surface shapes and features.
\begin{figure}[h]
    \centering
    \subcaptionbox{Asteroid Itokawa\label{fig:itokawa}}{\includegraphics[height=0.3\textheight,width=0.5\textwidth, keepaspectratio]{figures/eso1405b.jpg}}~
    \subcaptionbox{Comet 67/Churyumov-Gerasimenko\label{fig:67p}}{\includegraphics[height=0.3\textheight,width=0.5\textwidth,keepaspectratio]{figures/comet67pcgin.jpg}}
    \caption{Examples of the non-ellipsoidal shapes of small solar system bodies. Both asteroids and comets will tend to have vastly irregular shapes due to their low mass and violent histories of impacts and collisions~\label{fig:irregular_asteroids}}
\end{figure}
The scientific community describes asteroid shape using the facet-vertex model.
This approach is an efficient representation of the more general notion of a polyhedron from geometry.
Here we define the notion of the polyhedron and some specifics of the format used in the astrodynamics community.

A polyhedron is a generalization of a two-dimensional polygon to three-dimensions~\cite{orourke1998}.
It is the region of space with a boundary defined by a surface of a finite number of polygonal faces.
The surface of the polyhedron is composed of three types of primitive objects: zero-dimensional points called vertices, one-dimensional segments called edges, and two-dimensional polygons called faces or facets.
Furthemore, without any loss of generality we assume each face is a convex polygon since any nonconvex face can be divided into smaller convex faces.
A valid polyhedron in the context of asteroid shape models must satisfy several constraints.
These constraints define the relationship between each of the types of primitives which make up the polyhedron surface.
The primitives must intersect ``properly'', the local and global topology must be ``proper''.
For asteroid shape model we further assume that each face is a triangular polygon. 
Again, this does not limit generality as any polygon can be divided into a series of planar triangles.

@@

\subsubsection{Wavefront OBJ files}
The OBJ format is a geometry definition file format used for a variety of computer modeling applications, and is regularly used by the asteroid community~\cite{neese2004}.
The basic format of the file is an ASCII file where the first \( N_v\) lines begin with \texttt{v} and define the three components of a vertex in the body fixed reference frame.
The following \( N_f\) lines begin with \texttt{f} and define the three indices of the vertices that make up the face.
The numbering of the vertices is implicitly defined by the order listed in the file, i.e. the vertices are defined from \( 1 \) to \( N_v\).
There are two main assumptions used by the asteroid community.
First, each face is triangular and second, the vertices are numbered in a counterclockwise fashion about each face.
This allows the outward facing normal to each face to be uniquely defined without any additional data.
